---
title: "Homework 4"
author: "Bridget Antwiwaa"
date: "2/22/2022"
output: word_document
---
```{r}
data1=read.csv(choose.files(), header = T)
data2=data1[,c("earnings","height")]
```

**Qa**
```{r}
median(data1$height)
```

**Qb**

**i**
```{r}
short= data2$earnings[data1$height<=67]
mean(short)
```

**ii**
```{r}
tall=data2$earnings[data1$height>67]
mean(tall)
```

**iii**

On average taller workers earn more than shorter workers by $5499.44.

```{r}
t.test(x=tall, y=short, var.equal = T)
```

The 95% confidence is (4707.007, 6291.873)

**Qc**
```{r}
plot(x=data1$height, y=data1$earnings, xlab = "height", ylab = "earnings", main = "Scatter plot of earning on height ", pch=21, bg="purple")
```

The points fall along a horizontal line with only 23 disticnt values of earnings is because the data was collected in 23 brackets.

**Qd**
```{r}
reg1=lm(earnings~height, data = data2)
summary(reg1)
reg1$coefficients
```

The estimated slope is 707.6716 

**worker who is 67, 70, 65: earning= 707.6716height + (-512.7336)**

```{r}
707.6716*(67) + (-512.7336)

707.6716*(70) + (-512.7336)

707.6716*(65) + (-512.7336)
```

**Qe**
```{r}
height.cm=data2$height*(2.54)
reg.height.cm= lm(earnings~height.cm, data = data2)
summary(reg.height.cm)
reg.height.cm$coefficients
```

**i**
The estimated slope is 278.6108

**ii**
The estimated intercept is -512.7336

**iii**
R^2 is 0.01088

**iv**
SER is 19.88

**Qf**
```{r}
femData=subset(data1,sex==0)
reg2=lm(earnings~height, data = femData)
summary(reg2)
```

**i**
The slope intercept is  511.2222

**ii**
```{r}
mean(femData$height)
```

**average women**
```{r}
12650.8577+511.2222*(64.49278) 
```

**randomly selected women 1 in taller than average**
```{r}
64.49278+1
12650.8577+511.2222*(65.49278)
```

You would predict that her earnings would be higher than the average by $511.22

**Qg**
```{r}
maleData=subset(data1,sex==1)
reg3=lm(earnings~height, data = maleData)
summary(reg3)
```

The estimated slope is 1306.86

**mean for men**
```{r}
mean(maleData$height)
```

**average male**
```{r}
-43130.34 +1306.86*(70.08409)
```

**randomdly selected male 1 in taller than average**
```{r}
70.08409+1
-43130.34 +1306.86*(71.08409)
```

You would predict that his earnings would be higher than the average by $1306.86

**Qh**

Yes I do think that height is uncorrelated with the other factors that cause earnings. Therefore, the regression error term has a conditional mean of zero given height.  

#Chapter 5

**Qa**
```{r}
reg1=lm(earnings~height, data = data2)
summary(reg1)
```

**ii**

looking at the t-value (14.016), we reject the null making the estimated slope statisticaly significant 

**ii**
```{r}
707.6716+1.96*(50.49)
707.6716-1.96*(50.49)
```

The confidence interval is (608.7112,806.632)

**Qb**
```{r}
femData=subset(data1,sex==0)
reg2=lm(earnings~height, data = femData)
summary(reg2)
```

looking at the t value (5.169), we reject the null so it is statistically significant

**ii**
```{r}
511.2222 +1.96*(98.9)
511.2222 -1.96*(98.9)
```

The confidence interval is (317.3782,705.0662)

**Qc**
```{r}
maleData=subset(data1,sex==1)
reg3=lm(earnings~height, data = maleData)
summary(reg3)
```

looking at the t value (12.969), we reject the null so it is statistically significant

**ii**
```{r}
1306.86  +1.96*(100.8)
1306.86  -1.96*(100.8)
```

The confidence interval is (1109.292,1504.428)

**Qe**

Occupation1_height = contruction/minning(11)

Occupation1_no.height = Administrat(5)

```{r}
construction.Data=subset(data1,occupation==11)
reg4=lm(earnings~height, data = construction.Data)
summary(reg4)
```

```{r}
Administrat.Data=subset(data1,occupation==5)
reg5=lm(earnings~height, data = Administrat.Data)
summary(reg5)
```

The t-value for workers that require height (contruction) is 3.155, we reject the null so it is statistically significant. However, if you look at the t-value for workers that do not require height (Administrat), it is around 1.505 which we fail to reject the null so it is not statistically signnificant. With the 2 conclusion and the previous regressions, the effect of height on earnings does disappear when the sample is restricted to occupations in which strength is unlikely to be important.   